```{r data generation, echo = FALSE, results = "hide"}
n <- rpois(1, 22)
mu    <- rpois(1, 150)
sigma <- as.integer(runif(1, 5, 15))

x         <- round(mean(rnorm(n, mu, sigma)), digits = 2)
qtiles    <- c(0.75, 0.80, 0.90, 0.95, 0.99)
qtile_idx <- sample(1:length(qtiles), 1)
qtile     <- qtiles[qtile_idx]
not_qtile <- sample(qtiles[-qtile_idx], 1)
solution  <- round(qnorm(qtile, mu, sigma / sqrt(n)), digits = 3)
```



Question
========

`r n` University of Arkansas pre-law students are taking the LSAT exam (the standardized exam for entry into law school) where the average LSAT score in the United States is `r mu` with a standard devation of `r sigma`. To be a top-ranked institution, the average student score must be in the in the top `r fmt(qtile * 100, digits = 0)`\% of classes. What average score is needed for the University to be a top ranked school?


Below is `R` code for the problem that can be used to solve the problem.

<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>


<!-- The code below works well for html formats -->

<div class="col2">


<pre><code>
qnorm(`r not_qtile`, 0, 1)
</code></pre>

```{r, eval=TRUE, echo=FALSE}
cat(fmt(round(qnorm(not_qtile, 0, 1), digits = 3), digits = 3))
```


<pre><code>
qnorm(`r mu`, `r not_qtile * 100`, `r sigma`)
</code></pre>


```{r, eval=TRUE, echo=FALSE}
cat(fmt(round(pnorm(mu, qtile * 100, sigma), digits = 3), digits = 3))
```

<pre><code>
qnorm(`r qtile`, 0, 1)
</code></pre>


```{r, eval=TRUE, echo=FALSE}
cat(fmt(round(qnorm(qtile, 0, 1), digits = 3), digits = 3))
```

<pre><code>
qnorm(`r qtile * 100`, `r mu`, `r sigma`)
</code></pre>

```{r, eval=TRUE, echo=FALSE}
cat(fmt(round(pnorm(qtile * 100, mu, sigma), digits = 3), digits = 3))
```

</div>


Solution
========

The Z-score for the average students' scores are $Z =$ `qnorm(``r qtile``)` $= `r round(qnorm(qtile), digits = 3)`$. From the Z-score, we can calculate the LSAT score needed by solving $Z = \frac{\bar{x} - \mu}{\frac{\sigma}{\sqrt{n}}}$ for $\bar{x}$ getting $\bar{x} = Z * \frac{\sigma}{\sqrt{n}} + \mu = `r round(qnorm(qtile), digits = 3)` * `r sigma` / `r round(sqrt(n), digits = 3)` + `r mu` = `r solution`$.




Meta-information
================
extype: num
exsolution: `r solution`
exname: clt-quantile3
tol: 0.05