```{r, echo = FALSE, results = "hide"}
## possible answers
possible <- c(
    "glimpse()",
    "str()",
    "print()",
    "summary()",
    "c()",
    "lm()",
    "inspect()", 
    "modify()",
    "simulate()"
)

solutions <- c(TRUE, TRUE, rep(FALSE, length(possible) - 2))
## permute order of solutions/questions
o <- sample(1:length(possible), 5)
while (sum(solutions[o]) == 0) {
    ## make sure there is at least one correct answer
    o <- sample(1:length(possible), 5)    
}

questions <- possible[o]
solutions <- solutions[o]
```

Question
========


Which of the following `R` functions allows you a quick, overview of the data? Make sure you select all that apply.

```{r, echo = FALSE, results = "asis"}
answerlist(questions)
```


Solution
========
The answer is `r c("(a)", "(b)", "(c)", "(d)", "(e)")[which(solutions)]`. The functions `glimpse()`, `str()` and `summary()` print out quick overviews of the data giving the number of varaibles, type of variables, and other quick previews of the data. The function `print()` gives an overview of the data, however the output is not summarized or does `print()` return a quick overview. The functions `lm()`, `c()`, `modify()`, and `simulate()` do not display the data at all .



Meta-information
================
extype: mchoice
exsolution: `r mchoice2string(solutions)`
exname: glimpse-str


