```{r, echo = FALSE, results = "hide"}
## DATA GENERATION
n <- 5#sample(4:6, 1)
d <- 3#sample(2:4, 1)
y <- matrix(sample(1:10, n * d, replace = TRUE), n, d)

## check if any rows are duplicates
while(any(duplicated(y))) {
    y <- matrix(sample(1:10, n * d, replace = TRUE), n, d)
}
## Still under development
possible <- list(
    y[1, ],
    y[2, ],
    y[3, ],
    y[4, ],
    y[, 1],
    y[, 2]
)
    

correct <- 2
solutions <- c(rep(FALSE, 4), TRUE)
o <- c(sample((1:length(possible))[-correct], 4), correct)

    
## permute order of solutions/questions
shuffle <- sample(1:5)
questions <- possible[o][shuffle]
solutions <- solutions[shuffle]
```

Question
========


Below is some `R` code. The matrix $y$ is displayed below.

```{r}
y
```

What is the output at the end of running the code?

```{r , echo = TRUE, results = "hide"}
y[2, ]
```

Which of the following statements are correct?

```{r, echo = FALSE, results = "asis"}
answerlist(questions, markup = "markdown")
```


Solution
========

The answer is `r c("(a)", "(b)", "(c)", "(d)", "(e)")[which(solutions)]` because the output is the 2nd row of the matrix $y = \begin{pmatrix} `r y[1, ]` \\ \hlight{`r y[2, ]`} \\ `r y[3, ]`\\ `r y[4, ]` \\ `r y[5]` \\ \end{pmatrix}$ is $\begin{pmatrix} `r y[2, ]` \end{pmatrix}$.

\vspace{3cm}



<!-- ```{r, echo = FALSE, results = "asis"} -->
<!-- answerlist(solutions) -->
<!-- ``` -->




Meta-information
================
extype: schoice
exsolution: `r mchoice2string(solutions, single = TRUE)`
exname: matrix-subset


