```{r, echo = FALSE, results = "hide"}
## DATA GENERATION
y <- 5
x <- 3 * y
y <- 2 * y + 3
## Still under development
possible <- c(
    y - 2,
    y - 4,
    x,
    y,
    16
)
    

correct <- 1
solutions <- c(rep(FALSE, 4), TRUE)
o <- c(sample((1:length(possible))[-correct], 4), correct)

    
## permute order of solutions/questions
shuffle <- sample(1:5)
questions <- possible[o][shuffle]
solutions <- solutions[shuffle]
```

Question
========


Below is some `R` code. What is the output at the end of running the code?

```{r , echo = TRUE, results = "hide"}
y <- 5
x <- 3 * y
y <- 2 * y + 3
y - 2
```

Which of the following statements are correct?

```{r, echo = FALSE, results = "asis"}
answerlist(questions)
```


Solution
========

The answer is `r c("(a)", "(b)", "(c)", "(d)", "(e)")[which(solutions)]`. The final line is $y - 2$ so we need to find the value of $y$ at the end of the code. We initially assign $y$ the value of $5$. Next, we assign $x$ the value $15 = 3 * 5$. Next, we assign $y$ the value $2 * {\color{red}y} + 3 = 2 * {\color{red}5} + 3 = 13$ because the previous value of $y$ was 5. Finally, we print out the value $y - 2 = 11$.


<!-- ```{r, echo = FALSE, results = "asis"} -->
<!-- answerlist(solutions) -->
<!-- ``` -->




Meta-information
================
extype: schoice
exsolution: `r mchoice2string(solutions, single = TRUE)`
exname: variable-assignment


