```{r, echo = FALSE, results = "hide"}
## DATA GENERATION
n <- 4#sample(4:6, 1)
d <- 1#sample(2:4, 1)
x <- c(2 * (1:4))
y <- c(1:4)

## check if any rows are duplicates

## Still under development
possible <- c(
    "x * y",
    "x + y",
    "x - y",
    "x / y",
    "2 * x * y"
)
    

correct <- 2
solutions <- c(rep(FALSE, 4), TRUE)
o <- c(sample((1:length(possible))[-correct], 4), correct)

    
## permute order of solutions/questions
shuffle <- sample(1:5)
questions <- possible[o][shuffle]
solutions <- solutions[shuffle]
```

Question
========


The following are two vectors

```{r}
x
y
```

What is the code that generates the following output?

```{r, echo = FALSE}
x + y
```


```{r, echo = FALSE, results = "asis"}
answerlist(questions)
```


Solution
========

The answer is `r c("(a)", "(b)", "(c)", "(d)", "(e)")[which(solutions)]` because vector addition $x + y = \begin{pmatrix} `r x[1]` \\ `r x[2]` \\ `r x[3]` \\`r x[4]`  \end{pmatrix} + \begin{pmatrix} `r y[1]` \\ `r y[2]`  \\ `r y[3]` \\ `r y[4]` \end{pmatrix} = \begin{pmatrix} `r x[1]` + `r y[1]` \\ `r x[2]` + `r y[2]` \\ `r x[3]` + `r y[3]` \\ `r x[4]` + `r y[4]` \end{pmatrix} = \begin{pmatrix} `r x[1] + y[1]` \\ `r x[2] + y[2]` \\ `r x[3] + y[3]` \\ `r x[4] + y[4]` \end{pmatrix}$.

\vspace{3cm}



<!-- ```{r, echo = FALSE, results = "asis"} -->
<!-- answerlist(solutions) -->
<!-- ``` -->




Meta-information
================
extype: schoice
exsolution: `r mchoice2string(solutions, single = TRUE)`
exname: vector-operation


